14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-19 rules/rules19.tex
Added challenge track logics.

  \item {\bf New \challtrack.}
    This year, we introduce a new \challtrack.  This track will contain
    new challenging SMT-LIB benchmarks (with an emphasis on industrial
    applications) that are either unsolved or unsolved within some reasonable
    time limit, as indicated by the benchmark submitters.  We will also include
    benchmarks nominated by the community as challenging and of interest. In
    this track, solvers will run with a significantly longer time limit.
    \rationale{ Different application domains require different time limits.
    For example software verification traditionally requires much lower time
    limits, compared to hardware verification.  To reward solvers optimized for
    different use cases, we propose this new track and a new score for
    benchmarks solved within a very low time limit (see item ``New Scores in
    the \maintrack'').  } See ~\ref{sec:exec:industry-challenge} for the list of
    benchmark families included in \challtrack for this year.

@@

\todo{time limit}
The \challtrack will include both incremental and single query benchmarks and it will follow the same rules as the \inctrack and  \maintrack, respectively with two exceptions: benchmark selection and the time limit. The track will run on challenging industrial benchmarks provided by the community. This year, the \challtrack will include all the benchmarks from the \lh{TODO families} families, in the \lh{TODO logics}.

>>>>

  \item {\bf New \challtrack.}
    This year, we introduce a new \challtrack.  This track will contain
    new challenging SMT-LIB benchmarks (with an emphasis on industrial
    applications) that are either unsolved or unsolved within some reasonable
    time limit, as indicated by the benchmark submitters.  We will also include
    benchmarks nominated by the community as challenging and of interest. In
    this track, solvers will run with a significantly longer time limit.
    \rationale{ Different application domains require different time limits.
    For example software verification traditionally requires much lower time
    limits, compared to hardware verification.  To reward solvers optimized for
    different use cases, we propose this new track and a new score for
    benchmarks solved within a very low time limit (see item ``New Scores in
    the \maintrack'').  } See ~\ref{sec:exec:industry-challenge} for the logics
    included in \challtrack for this year.

@@

\todo{time limit}
The \challtrack will include both incremental and single query benchmarks and
it will follow the same rules as the \inctrack and  \maintrack, respectively
with two exceptions: benchmark selection and the time limit. The track will
run on challenging industrial benchmarks provided by the community. This year,
the \challtrack will include both incremental and single query benchmarks in the
following logics QF\_BV, QF\_ABV and QF\_AUFBV. The complete list of benchmarks
along with instructions on how to access them will be provided on the SMT-COMP
website as soon as the benchmarks are released.
